---
output:
  govdown::govdown_document:
    page_title: "CSPS 2019: Benchmark results"
    css: style.css
---

<script src="https://ajax.googleapis.com/ajax/libs/jquery/3.5.1/jquery.min.js"></script>


``` {js echo=FALSE}
<!-- Add custom styles-->

$('head').append('<link rel="stylesheet" href="style.css" type="text/css" />');

```


``` {r setup, include=FALSE}

library(tidyverse)

options(knitr.kable.NA = "")

diff_postproc <- function(str, x) {
  
  fmt <- case_when(
    is.na(x) | x < 0 ~ "%s",
    x == 0 ~ "=",
    x > 0 ~ "+%s")
  
  sprintf(fmt, str)
  
}

diff_formatter <- function(x, digits = 0L, format = "f", big.mark = ",", ...) {
  
  formattable::formattable(janitor::round_half_up(as.numeric(x)), 
                           format = format, 
                           big.mark = big.mark,
                           digits = digits, 
                           ..., 
                           postproc = "diff_postproc")
}

bold_formatter <- function(x) {
  paste0("**", x, "**")
}

csps_median_all <- read_csv("data/csps_median.csv")

csps_median_2019_summary <- csps_median_all %>%
  filter(year == 2019, theme == "SUMMARY") %>%
  arrange(sortorder) %>%
  pull(value) %>%
  formattable::percent(digits = 0)

names(csps_median_2019_summary) <- csps_median_all %>%
  filter(year == 2019, theme == "SUMMARY") %>%
  arrange(sortorder) %>%
  pull(measure)

csps_median_2018_summary <- csps_median_all %>%
  filter(year == 2018, theme == "SUMMARY") %>%
  arrange(sortorder) %>%
  pull(value) %>%
  formattable::percent(digits = 0)

names(csps_median_2018_summary) <- csps_median_all %>%
  filter(year == 2018, theme == "SUMMARY") %>%
  arrange(sortorder) %>%
  pull(measure)

csps_median_2019_summary_diff <- ((csps_median_2019_summary - 
                               csps_median_2018_summary) * 100) %>%
  diff_formatter()

names(csps_median_2019_summary_diff) <- names(csps_median_2019_summary)


```


# Civil Service benchmark results

The Civil Service benchmark results are the overall headline results from the Civil Service People Survey, they are calculated as the median (mid-point) of participating organisations' scores for each measure.

``` {r summary, echo=FALSE, warning=FALSE}

summarytbl <- csps_median_all %>%
  filter(theme == "SUMMARY") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-measure, -sortorder, -theme) %>%
  mutate_at(vars(-label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter)

summarytbl_names <- names(summarytbl) %>%
  str_replace("label", "")

summarytbl %>% knitr::kable(format = "markdown", col.names = summarytbl_names)

```


::: {.accordion}
## My work


``` {r mw, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "MW") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## Organisational objectives and purpose


``` {r op, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "OP") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## My manager


``` {r lm, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "LM") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## My team


``` {r mt, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "MT") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## Learning and development


``` {r ld, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "LD") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## Inclusion and fair treatment


``` {r inc, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "IF") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## Resources and workload


``` {r rw, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "RW") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## Pay and benefits


``` {r pb, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "PB") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## Leadership and managing change


``` {r lc, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "LC") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## Employee engagement


``` {r ee, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "EE") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## Taking action


``` {r ta, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "TA") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## Organisational culture


``` {r oc, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "OC") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## The Civil Service Vision and Leadership Statement


``` {r vl, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "VL") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## Future intentions

**C01. Which of the following statements most reflects your current thoughts about working for [your organisation]?**

``` {r fi, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "FI") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Response` = label) %>%
  knitr::kable(format = "markdown")

```


## The Civil Service Code


``` {r cs, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "CS") %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```


## Discrimination

**E01. Have you been discriminated against at work, in the past 12 months?**

``` {r e01, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(str_detect(measure, "E01")) %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  mutate(label = case_when(
    measure == "E01_YES" ~ "Yes",
    measure == "E01_NO" ~ "No",
    measure == "E01_PNS" ~ "Prefer not to say")) %>%
  rename(`#` = measure, `Response` = label) %>%
  knitr::kable(format = "markdown")

```

**E02. On which of the following grounds were you discriminated against?**

:::{.small-para}
Asked only of those who answered yes at E01. Multiple selection was allowed, therefore the result is shown as a proportion of those who said yes to E01 and may sum to more than 100%.
:::

``` {r e02, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(str_detect(measure, "E02")) %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  mutate(label = str_remove_all(label, "^Grounds of discrimination: ")) %>%
  rename(`#` = measure, `Response` = label) %>%
  knitr::kable(format = "markdown")

```



## Bullying and harassment

**E03. Have you been bullied or harassed at work, in the past 12 months?**

``` {r e03, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(str_detect(measure, "E03_")) %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  mutate(label = case_when(
    measure == "E03_YES" ~ "Yes",
    measure == "E03_NO" ~ "No",
    measure == "E03_PNS" ~ "Prefer not to say")) %>%
  rename(`#` = measure, `Response` = label) %>%
  knitr::kable(format = "markdown")

```

**E03A. How would you describe the nature of the bullying and/or harassment you experienced?**

:::{.small-para}
Asked only of those who answered yes at E03. Multiple selection was allowed, therefore the result is shown as a proportion of those who said yes to E03 and may sum to more than 100%.
:::

``` {r e03a, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(str_detect(measure, "E03A")) %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  mutate(
    label = str_remove_all(label, "^Nature of bullying and/or harassment: ")
  ) %>%
  rename(`#` = measure, `Response` = label) %>%
  knitr::kable(format = "markdown")

```

**E04. Who bullied and/or harassed you?**

:::{.small-para}
Asked only of those who answered yes at E03. Multiple selection was allowed, therefore the result is shown as a proportion of those who said yes to E03 and may sum to more than 100%.
:::

``` {r e04, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(str_detect(measure, "E04")) %>%
  arrange(year, sortorder) %>%
  pivot_wider(names_from = year, values_from = value) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  mutate(
    label = str_remove_all(label, "^Who bullied and/or harassed you\\?: ")
  ) %>%
  arrange(measure) %>%
  rename(`#` = measure, `Response` = label) %>%
  knitr::kable(format = "markdown")

```


**E05. Did you report your experience of bullying and/or harassment?**

:::{.small-para}
Asked only of those who answered yes at E03. In 2019, multiple selection was allowed under the “Yes” and “No” subheadings, therefore these results are shown as a proportion of those who answered “Yes” or “No” and may not sum to 100%.
:::

``` {r e05_1, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(str_detect(measure, "E05_\\D")) %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  mutate(label = case_when(
    measure == "E05_YES" ~ "Any yes response",
    measure == "E05_NO" ~ "Any no response",
    measure == "E05_PNS" ~ "Prefer not to say")) %>%
  rename(`#` = measure, `Response` = label) %>%
  knitr::kable(format = "markdown")

```


``` {r e05_2, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(str_detect(measure, "E05_\\d")) %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  mutate(
    label = str_remove_all(label, "^Reporting action/inaction: "),
    label = case_when(
      measure == "E05_01" | measure == "E05_02" | 
        measure == "E05_03" ~ paste("Yes: ", label),
      measure == "E05_04" | measure == "E05_05" | 
        measure == "E05_05" | measure == "E05_06" | 
        measure == "E05_07" | measure == "E05_08" | 
        measure == "E05_09" ~ paste("No: ", label),
    )
  ) %>%
  rename(`#` = measure, `Response` = label) %>%
  knitr::kable(format = "markdown")

```

**E06. How would you describe your situation now?**

:::{.small-para}
Asked only of those who answered yes at E03.
:::

``` {r e06, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(str_detect(measure, "^E06"), year == 2019) %>%
  mutate(
    response = case_when(
      str_detect(measure, "YES") ~ "Yes",
      str_detect(measure, "NO") ~ "No",
      str_detect(measure, "PNS") ~ "Prefer not to say"),
    measure = str_remove(measure, "_YES|_NO|_PNS")) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme, -year) %>%
  pivot_wider(names_from = response, values_from = value) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  rename(`#` = measure, `Question` = label) %>%
  knitr::kable(format = "markdown")

```



## Wellbeing


``` {r wb_w, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(str_detect(measure, "^W0")) %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  rename(`#` = measure, `Question/Measure` = label) %>%
  knitr::kable(format = "markdown")

```

**Wellbeing indices**

``` {r wb_ind, echo=FALSE, warning=FALSE}

csps_median_all %>%
  filter(theme == "WB", str_detect(measure, "^W0", negate = TRUE)) %>%
  pivot_wider(names_from = year, values_from = value) %>%
  arrange(sortorder) %>%
  select(-sortorder, -theme) %>%
  mutate_at(vars(-measure, -label), formattable::percent, digits = 0) %>%
  mutate_at(vars(`2019`), bold_formatter) %>%
  mutate(label = str_remove_all(label, "^Wellbeing: ")) %>%
  rename(`#` = measure, `Question/Measure` = label) %>%
  knitr::kable(format = "markdown")

```


:::

---



``` {js echo=FALSE}
<!-- Add jQuery post-processing -->

$(".govuk-table").addClass("govuk-!-font-size-16")

```
