---
title: "Benchmark scores"
custom_title: "Civil Service benchmark scores 2009 to 2020"
date: 2022-04-25
section: results
weight: 100
summary: "The Civil Service People Survey benchmark (median) scores over time"
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)

data_dir <- file.path(dirname(getwd()), "data")

svg_spark <- function(values, height = 20, width = 80) {
  
  values <- as.numeric(values)
  values <- values[!is.na(values)]
  
  y_values <- round(scales::rescale(-values, to = c(1, height - 1)))
  x_values <- round(scales::rescale(seq(length(values)), to = c(1, width - 3)))
  
  coords <- paste(x_values, y_values, sep = ",", collapse = " ")
  
  poly_coords <- paste(
    paste(min(x_values), max(y_values), sep = ","),
    coords,
    paste(max(x_values), max(y_values), sep = ","),
    paste(min(x_values), max(y_values), sep = ","))
  
  x <- htmltools::tags$svg(
    height = height,
    width = width,
    htmltools::tags$polygon(
      points = poly_coords,
      style = "fill:#1d70b840;stroke:none;"
    ),
    htmltools::tags$polyline(
      points = coords,
      style = "fill:none;stroke:#1d70b8;stroke-width:2"
    ),
    htmltools::tags$circle(
      cx = x_values[length(x_values)],
      cy = y_values[length(y_values)],
      r = "2%",
      style = "fill:#1d70b8;stroke:none;"
    )
  )
  
  return(as.character(x))
  
}

csps2020_median_ts <- readr::read_csv(
  file.path(data_dir, "csps2020_median_timeseries.csv")
) %>%
  janitor::clean_names()

csps2020_sparks <- csps2020_median_ts %>%
  select(measure, x2009:x2020) %>%
  pivot_longer(cols = -measure, names_to = "year") %>%
  drop_na(value) %>%
  group_by(measure) %>%
  summarise(
    spark = svg_spark(c(value))
  )

csps2020_ts_out <- csps2020_median_ts %>%
  left_join(csps2020_sparks, by = "measure") %>%
  mutate(
    sort_order = row_number(),
    out_label = case_when(
      str_detect(measure, "E01_|E03_") ~ label,
      str_detect(measure, "EES|_index", negate = TRUE) & section != "Theme scores" ~
        str_remove_all(label, " \\(%.*"),
      section == "Theme scores" ~ str_remove_all(label, "theme score.*"),
      str_detect(measure, "EES|") ~ str_remove_all(label, " \\(.*")
    ),
    section = if_else(measure == "EES", "Theme scores", section),
    section = as_factor(section),
    out_label = as_factor(out_label)
  ) %>%
  select(section, measure = out_label, x2009:x2020, spark)

csps2020_ts_sd <- crosstalk::SharedData$new(csps2020_ts_out)

fs_section <- crosstalk::filter_select(
  id = "filter-section",
  label = "Survey section",
  sharedData = csps2020_ts_sd,
  group ~section,
  multiple = FALSE,
)

fs_measure <- crosstalk::filter_select(
  id = "filter-measure",
  label = "Survey measure/question",
  sharedData = csps2020_ts_sd,
  group ~measure,
  multiple = TRUE,
)

```

The Civil Service benchmark is the median score of the participating organisations each year. The table below shows the benchmark scores for all measures and questions in the survey from 2009 to 2020, though not all questions have been asked since the start of the survey. You can filter by survey section and/or for individual measures.

::::{.govuk-grid-row .data-card}

:::{.govuk-grid-column-one-quarter .data-filters .govuk-body-s}
```{r selectors, echo=FALSE}
govukhugo::unstrap(fs_section)
govukhugo::unstrap(fs_measure)
govukhugo::clear_filters()
```
:::

:::{.govuk-grid-column-three-quarters .data-display}
```{r table}

govukhugo::govuk_datatable(
  csps2020_ts_sd,
  col_names = c("Section", "Measure", 2009:2020, "Trendline"),
  small_text = TRUE,
  search = FALSE,
  col_defs = list(
    list(visible = FALSE, targets = list(0))
  ),
  copy_info = "Civil Service benchmark scores 2009-2020",
  export_file = "csps2020_benchmark_scores.csv"
) %>%
  DT::formatPercentage(columns = 3:14, digits = 0)

```
:::

::::

{{< break type="m" >}}

{{< details "Notes" >}}
{{< small >}}Please note that the trend lines presented in this table are relative. As a result, trend lines for measures with very little variation in their benchmark score may present an exaggerated picture of the changes over time.{{< /small >}}
{{< /details >}}
